Exploring the Validity Range of PLL Analytical Models

### 2025-06-04 CaseStudies/Example3_2_LimitsoftheTheorySoFar/Report/article/article.qmd
Finishing example.

# Parâmetros iniciais
f_r = 10e6 # Hz
omega_r = 2 * np.pi * f_r # rad/s
fvco = f_o = 50e6 # Hz
omega_o = 2 * np.pi * f_r # rad/s
N = 5
Kvco = KVCO = 10e6 # Hz/V
Kvco_ang = 2 * np.pi * Kvco # rad/s/V
I_CP = I = 1e-3
K_theta = Kphase = I / (2 * np.pi) # A/rad
A0 = 6.258
K = A0 * Kphase * KVCO / N
```

@@

| **Symbol**       | **Description**  | **Value**                                       |
|------------------|------------------|-------------------------------------------------|
| $C_1$            | Series capacitor | `{python} format(C_1)`F                         |
| $R_1$            | Series resistor  | `{python} format(R_1)`$\Omega$                  |
| $C_2$            | Shunt capacitor  | `{python} format(C_2)`F                         |
| $f_\mathrm{VCO}$ | VCO freq.        | `{python} format(fvco)`Hz                       |
| $K_\mathrm{VCO}$ | VCO sensivity    | `{python} format(Kvco)`Hz/V                     |
| $\theta_{e_m}$   | Max. Phase Error | `{python} format_with_pi_latex(theta_e_m)`rad   |
| $I_\mathrm{CP}$  | CP Current       | `{python} format(I_CP)`A                        |
| $A_0$            | DC Gain          | `{python} format(A0)`                           |
| $f_\mathrm{bw}$  | Bandwidth        | `{python} format(f_bw)`Hz                       |
| $f_r$            | Ref. freq.       | `{python} format(f_r)`Hz                        |
| $N$              | Divider          | `{python} format(N)`                           |
| $\Delta f_m$     | Max. Step freq.  | `{python} format(step_m_lin)`Hz                 |
| $t_s$            | Settling time    | `{python} format(t_s)`s                         |

>>>>

# Parâmetros iniciais
f_r = 10e6 # Hz
omega_r = 2 * np.pi * f_r # rad/s
fvco = f_o = 50e6 # Hz
omega_o = 2 * np.pi * f_r # rad/s
N = 5
Kvco = KVCO = 2 * np.pi * 10e6 # rad/s/V
Kvco_lin = Kvco / (2 * np.pi) # Hz/V
I_CP = I = 1e-3
K_theta = Kphase = I / (2 * np.pi) # A/rad
A0 = 1
K = A0 * Kphase * KVCO / N
```

@@

| **Symbol**       | **Description**  | **Value**                                       |
|------------------|------------------|-------------------------------------------------|
| $C_1$            | Series capacitor | `{python} format(C_1)`F                         |
| $R_1$            | Series resistor  | `{python} format(R_1)`$\Omega$                  |
| $C_2$            | Shunt capacitor  | `{python} format(C_2)`F                         |
| $f_\mathrm{VCO}$ | VCO freq.        | `{python} format(fvco)`Hz                       |
| $K_\mathrm{VCO}$ | VCO sensivity    | `{python} format(Kvco_lin)`Hz/V                     |
| $\theta_{e_m}$   | Max. Phase Error | `{python} format_with_pi_latex(theta_e_m)`rad   |
| $I_\mathrm{CP}$  | CP Current       | `{python} format(I_CP)`A                        |
| $A_0$            | DC Gain          | `{python} format(A0)`                           |
| $f_\mathrm{bw}$  | Bandwidth        | `{python} format(f_bw)`Hz                       |
| $f_r$            | Ref. freq.       | `{python} format(f_r)`Hz                        |
| $N$              | Divider          | `{python} format(N)`                           |
| $\Delta f_m$     | Max. Step freq.  | `{python} format(step_m_lin)`Hz                 |
| $t_s$            | Settling time    | `{python} format(t_s)`s                         |
